### 2022-11-24 ms.rmd
New tree

```{r, tree}
# Bring in the fly tree
tree <- read.tree("./phylogeny/drosi.tre")

@@

# Ultrametric?
is.ultrametric(tree) # nope

# Grab phylo matrix
phy_vcv <- vcv(tree)

@@

>>>>

```{r, tree}
# Bring in the fly tree
tree <- read.tree("./phylogeny/drosi2.tre")

@@

# Ultrametric?
is.ultrametric(tree) # nope
tree2 <- force.ultrametric(tree, method = "extend")

# Grab out data
   data <- read.csv("./data/drosi_data.csv")

# functions
source("./R/func.R")
t <- tree_checks(tree2, data = data, dataCol = "species", type = "check")
data <- data %>% mutate(species = gsub(" ", "", species),
                        phylo = species,
                        obs = 1:n()) %>% filter(!species %in% t$Species_InData_But_NotTree) 
tree3 <- tree_checks(tree2, data = data, dataCol = "species", type = "prune")
tree_checks(tree3, data = data, dataCol = "species", type = "check")
# Grab phylo matrix
phy_vcv <- vcv(tree3, cor = FALSE)

@@

```{r}

## Model(s)
   ctmax <- bf(ctmax | se(sqrt(ctmax_se)) ~ 1 + (1|q|gr(phylo, cov = phy_vcv)) + (1|species) + (1|obs)) + gaussian()
    cfts <- bf( cfts |  mi() ~ 1 + (1|q|gr(phylo, cov = phy_vcv)) + (1|species)) + gaussian()
   #tdt_i <- bf(tdt_i |  mi() ~ 1 + (1|q|gr(phylo = phy_vcv)) + (1|spp)) + gaussian()
   tdt_z <- bf(tdt_z |  mi() ~ 1 + (1|q|gr(phylo, cov = phy_vcv)) + (1|species)) + gaussian()

       mv_brms_model <- brms::brm(ctmax + tdt_z + cfts, 
                        warmup = 1000, iter = 4000, thin = 5, 
                        control = list(adapt_delta = 0.95, max_treedepth = 15), cores = 4,
                        data = data, data2 = list(phy_vcv = phy_vcv))

#### Try MCMCglmm which I expect will be MUCH faster. Deals with missing data using data augmentation

prior = list(R = list(V = diag(3), nu=1.002), 
             G = list(G1=list(V = diag(3), nu = 1.002)))

data$animal = data$phylo

mcmcglmm_model <- MCMCglmm::MCMCglmm(cbind(ctmax, cfts, tdt_z) ~ -1 + trait, random = ~us(trait):animal, rcov = ~us(trait):units ,
                                     pedigree=tree3,
                                     burnin=1000, nitt = 300000, thin = 5, family = rep("gaussian", 3), prior = prior, 
                                    pl = TRUE, pr = TRUE, data = data)
saveRDS(mcmcglmm_model, file = "./output/model/mcmcglmm_model")
```
